Evaluating Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe using radiocarbon data

### 2019-03-28 article/02_Materials_and_Methods.Rmd
added repo doi

The code for this paper is written in the statistical programming language R [@rcoreteamLanguageEnvironmentStatistical2018] and fully reproducible [@marwickPackagingData2018]. It is available in a public Repository on GitHub (\url{https://github.com/nevrome/cultrans.bronzeageburials.article2019}) and with a permanent digital object identifier (DOI) on the Open Science Framework Platform (\url{doi}) A more in-depth description and discussion of the data preparation steps can be found in the master thesis this article is based on [@schmidComputerbasiertesCulturalEvolution2018].

>>>>

The code for this paper is written in the statistical programming language R [@rcoreteamLanguageEnvironmentStatistical2018] and fully reproducible [@marwickPackagingData2018]. It is available in a public Repository on GitHub (\url{https://github.com/nevrome/cultrans.bronzeageburials.article2019}) and with a permanent digital object identifier (DOI) on the Open Science Framework Platform (\url{http://dx.doi.org/10.17605/OSF.IO/B6NP2}) A more in-depth description and discussion of the data preparation steps can be found in the master thesis this article is based on [@schmidComputerbasiertesCulturalEvolution2018].
